Effects of Antenna Beam Chromaticity on Redshifted 21~cm Power Spectrum and Implications for Hydrogen Epoch of Reionization Array

### 2016-03-29 ForegroundSimulations/ms.tex
Remove commented lines
From d4fb025 (fgsim):
====================

In ms.tex,

(*) Remove commented lines

Since our aim in this paper is to quantify EoR-foreground power ratio without employing any sophisticated {\it foreground removal} techniques, we turn our attention to {\it foreground avoidance} strategy that employs spectral weighting technique. Specific choices for spectral weighting function, $W(f)$, have been found to be effective in reducing foreground contamination by many orders of magnitude \citep{thy13} and is regularly used in redshifted 21~cm data analysis \citep{par12a,par12b}. For instance, a {\it Blackman-Harris} function \citep{har78} has a dynamic range of $\sim$100 -- 120~dB in delay power spectrum and a reduced effective bandwidth, with:
\begin{align}\label{eqn:Beff}
  \epsilon &= \frac{1}{B} \int_{-B/2}^{+B/2} |W(f)|^2\,\dif f, \\
  \textrm{and,}\quad B_\textrm{eff} &= \epsilon\,B,
  % B_\textrm{eff} &= \int_{-B/2}^{+B/2} |W(f)|^2\,\dif f.
\end{align}
where, $B$ denotes the end-to-end range of the observing band, $1-\epsilon$ is the loss in overall spectral sensitivity and $B_\textrm{eff}$ is the effective bandwidth. The {\it noise equivalent width} is defined as $w_\textrm{ne}\equiv \sum_i |\widetilde{W}(\tau_i)|^2 / |\widetilde{W}(0)|^2$. For a {\it Blackman-Harris} window function denoted by $W_\textrm{BH}(f)$, $\epsilon \approx 50\%$ and $w_\textrm{ne} \approx 2$. % Hence, the window spans a total of $2N$ frequency channels each of width $\Delta f$ to have $B_\textrm{eff} \approx N\,\Delta f$.

@@

\begin{figure*}[htb]
\centering
\subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_150.0_MHz_subband.eps}}
\subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_150.0_MHz_subband.eps}} \\
\subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_170.0_MHz_subband.eps}}
\subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
\caption{Worst case EoR-foreground dynamic range, $\rho(\boldsymbol{b},f_0,\alpha)$, in {\it foreground avoidance} modes for different HERA-19 baselines as a function of RA ($\alpha$) of pointing on the sky. Each panel corresponds to the EoR model and subband indicated. The baseline vector is specified by its length (in m) and orientation (in degrees) at the bottom and top of the $x$-axis respectively. The color scale is logarithmic. Even in the worst case, HERA will be able detect EoR drawn from independent models on all baselines for a large fraction of a full 24~hour sky transit cycle. $\rho(\boldsymbol{b},f_0,\alpha)$ is seen to increase with increasing baseline length. This is because the loss in sensitivity to diffuse foreground power with increase in antenna spacings is faster than in the case of the EoR signal.}
\label{fig:eor-fg-ratios}
\end{figure*}

>>>>

Since our aim in this paper is to quantify EoR-foreground power ratio without employing any sophisticated {\it foreground removal} techniques, we turn our attention to {\it foreground avoidance} strategy that employs spectral weighting technique. Specific choices for spectral weighting function, $W(f)$, have been found to be effective in reducing foreground contamination by many orders of magnitude \citep{thy13} and is regularly used in redshifted 21~cm data analysis \citep{par12a,par12b}. For instance, a {\it Blackman-Harris} function \citep{har78} has a dynamic range of $\sim$100 -- 120~dB in delay power spectrum and a reduced effective bandwidth, with:
\begin{align}\label{eqn:Beff}
  \epsilon &= \frac{1}{B} \int_{-B/2}^{+B/2} |W(f)|^2\,\dif f, \\
  \textrm{and,}\quad B_\textrm{eff} &= \epsilon\,B,
\end{align}
where, $B$ denotes the end-to-end range of the observing band, $1-\epsilon$ is the loss in overall spectral sensitivity and $B_\textrm{eff}$ is the effective bandwidth. The {\it noise equivalent width} is defined as $w_\textrm{ne}\equiv \sum_i |\widetilde{W}(\tau_i)|^2 / |\widetilde{W}(0)|^2$. For a {\it Blackman-Harris} window function denoted by $W_\textrm{BH}(f)$, $\epsilon \approx 50\%$ and $w_\textrm{ne} \approx 2$.

@@

\begin{figure*}[htb]
  % \centering
  % \subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_150.0_MHz_subband.eps}}
  % \subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_150.0_MHz_subband.eps}} \\
  % \subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_170.0_MHz_subband.eps}}
  % \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
  \subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f6a.eps}}
  \subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f6b.eps}} \\
  \subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f6c.eps}}
  \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f6d.eps}}
  \caption{Worst case EoR-foreground dynamic range, $\rho(\boldsymbol{b},f_0,\alpha)$, in {\it foreground avoidance} modes for different HERA-19 baselines as a function of RA ($\alpha$) of pointing on the sky. Each panel corresponds to the EoR model and subband indicated. The baseline vector is specified by its length (in m) and orientation (in degrees) at the bottom and top of the $x$-axis respectively. The color scale is logarithmic. Even in the worst case, HERA will be able detect EoR drawn from independent models on all baselines for a large fraction of a full 24~hour sky transit cycle. $\rho(\boldsymbol{b},f_0,\alpha)$ is seen to increase with increasing baseline length. This is because the loss in sensitivity to diffuse foreground power with increase in antenna spacings is faster than in the case of the EoR signal.}
  \label{fig:eor-fg-ratios}
\end{figure*}
